---
title: "Metropolis Theme"
subtitle: "an ioslides presentation in R Markdown"
author: "JC Laria"
github: "jlaria.github.io"
date: "May 31, 2017"    
output: 
  ioslides_presentation:
    template: layout/default.html
    css: css/metropolis.css
    highlight: haddock
    smaller: no
    logo: img/logo.png
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = ' ', cache = TRUE)
```

## About

The [`metropolis`](github.com/matze/mtheme) theme is a Beamer theme with minimal visual noise
inspired by the `hsrm` Beamer Theme by Benjamin Weiss.

This is not the `metropolis` theme, but a customization to `ioslides` intended to look like `metropolis` to give a nice touch to R Markdown.

Enjoy it!

# Section 1

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


---

Slide with text only

## Slide with smaller{.smaller}

Hey, this is a small font-size.


# THANK YOU!
